---
title: "GIB in LVAD supported patients"
subtitle: "Research Letter"
author: "Salil Deo"
date: "`r Sys.Date()`"
output: tint::tintHtml


---

```{r setup, include=FALSE}
library(tint)
# invalidate cache when the package version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tint'))
options(htmltools.dir.version = FALSE)
```


gi bleeding on lvad support. trends and resource utilization

```{r get all dataframes, echo = FALSE, message = FALSE, warning = FALSE}

library(tidyverse);library(tidylog);library(haven);library(broom);library(survey)
library(srvyr);library(skimr);library(tidyr);library(tableone);library(janitor)

c10 <- read_sas("G:/lvad_gib/c2010_2.sas7bdat") # 2010

c11 <- read_sas("G:/lvad_gib/c2011_2.sas7bdat") # 2011

c12 <- read_sas('G:/lvad_gib/c2012_2.sas7bdat') # 2012

c13 <- read_csv("G:/lvad_gib/append13.csv") # 2013

c14 <- read_csv("G:/lvad_gib/append14.csv") # 2014

c15 <- read_csv("G:/lvad_gib/append15.csv") # 2015
```

get the important variables selected for each year and then to append them to create a single large dataframe for data modification and data analysis

```{r 2010}

#Testing with Salil

glimpse(c10)

names(c10) <- tolower(names(c10)) # change all var names to lowercase


c10.1 <- c10 %>%
  select(age,  amonth,  aweekend, died, discwt, dispuniform, totchg,
dqtr,   dx1, dx2, dx3,dx4, dx5, dx6, dx7, dx8, dx9, dx10, 
dxccs1, dxccs2, dxccs3, dxccs4, dxccs5,  female, 
hospid,  key, los, nis_stratum,  pay1,orproc,  pr1, pr2, pr3, pr4, pr5,  prccs1, prccs2,
prccs3, prccs4, prccs5, race, totchg,  year, zipinc_qrtl, lvad)



# get the original severity file from that year

s10 <- read_sas("G:/nis_2010_severity.sas7bdat")

names(s10) <- tolower(names(s10))

# then we will only select "cm" variables and "nis_stratum".
# this change has been made for testing only.

s10_s <- s10 %>% select(key, cm_aids:cm_wghtloss)

m10 <- left_join(c10.1, s10_s, by = "key")

glimpse(m10)

```


```{r 2011}

glimpse(c11)

names(c11) <- tolower(names(c11)) # change all var names to lowercase


c11.1 <- c11 %>%
  select(age,  amonth,  aweekend, died, discwt, dispuniform, totchg,
dqtr,   dx1, dx2, dx3,dx4, dx5, dx6, dx7, dx8, dx9, dx10, 
dxccs1, dxccs2, dxccs3, dxccs4, dxccs5,  female, 
hospid,  key, los, nis_stratum,  pay1,orproc,  pr1, pr2, pr3, pr4, pr5,  prccs1, prccs2, 
prccs3, prccs4, prccs5, race, totchg,  year, zipinc_qrtl, lvad)

# get the original core file from that year

s11 <- read_sas("G:/nis_2011_severity.sas7bdat")

names(s11) <- tolower(names(s11))

# then we will only select "cm" variables and "nis_stratum".



s11_s <- s11 %>% select(key, cm_aids:cm_wghtloss)

m11 <- left_join(c11.1, s11_s, by = "key")

glimpse(m11)

```


```{r 2012}

glimpse(c12)

names(c12) <- tolower(names(c12)) # change all var names to lowercase


c12.1 <- c12 %>%
  select(age,  amonth,  aweekend, died, discwt, dispuniform, totchg, 
dqtr,   dx1, dx2, dx3,dx4, dx5, dx6, dx7, dx8, dx9, dx10, 
dxccs1, dxccs2, dxccs3, dxccs4, dxccs5,  female, 
hosp_nis,  key_nis, los, nis_stratum,  pay1,orproc,  pr1, pr2, pr3, pr4, pr5,  prccs1, prccs2, 
prccs3, prccs4, prccs5, race, totchg,  year, zipinc_qrtl, lvad)


# get the original core file from that year

s12 <- read_stata("G:/NIS_2012_Severity.dta")

names(s12) <- tolower(names(s12))

# then we will only select "cm" variables and "nis_stratum".


s12_s <- s12 %>% select(key_nis, cm_aids:cm_wghtloss)

m12 <- left_join(c12.1, s12_s, by = "key_nis")

glimpse(m12)
```

```{r 2013}

glimpse(c13)

names(c13) <- tolower(names(c13)) # change all var names to lowercase


c13.1 <- c13 %>%
  select(age,  amonth,  aweekend, died, discwt, dispuniform, totchg,
dqtr,   dx1, dx2, dx3,dx4, dx5, dx6, dx7, dx8, dx9, dx10, 
dxccs1, dxccs2, dxccs3, dxccs4, dxccs5,  female, 
hosp_nis,  key_nis, los, nis_stratum,  pay1,orproc,  pr1, pr2, pr3, pr4, pr5,  prccs1, prccs2, 
prccs3, prccs4, prccs5, race, totchg,  year, zipinc_qrtl, lvad)

# get the original core file from that year

s13 <- read_stata("G:/NIS_DATA/nis2013/NIS_2013_Severity.dta")

names(s13) <- tolower(names(s13))

# then we will only select "cm" variables and "nis_stratum".


s13_s <- s13 %>% select(key_nis, cm_aids:cm_wghtloss)

m13 <- left_join(c13.1, s13_s, by = "key_nis")

glimpse(m13)

```


```{r 2014}

glimpse(c14)

names(c14) <- tolower(names(c14)) # change all var names to lowercase


c14.1 <- c14 %>%
  select(age,  amonth,  aweekend, died, discwt, dispuniform, totchg,
dqtr,   dx1, dx2, dx3,dx4, dx5, dx6, dx7, dx8, dx9, dx10, 
dxccs1, dxccs2, dxccs3, dxccs4, dxccs5,  female, 
hosp_nis,  key_nis, los, nis_stratum,  pay1,orproc,  pr1, pr2, pr3, pr4, pr5,  prccs1, prccs2, 
prccs3, prccs4, prccs5, race, totchg,  year, zipinc_qrtl, lvad)

# get the original core file from that year

s14 <- read_stata("G:/NIS_2014_Severity.dta")

names(s14) <- tolower(names(s14))

# then we will only select "cm" variables and "nis_stratum".


s14_s <- s14 %>% select(key_nis, cm_aids:cm_wghtloss)

m14 <- left_join(c14.1, s14_s, by = "key_nis")

glimpse(m14)
```



```{r 2015}

glimpse(c15)

names(c15) <- tolower(names(c15)) # change all var names to lowercase


c15.1 <- c15 %>%
  select(age,  amonth,  aweekend, died, discwt, dispuniform, totchg,
dqtr,   dx1, dx2, dx3,dx4, dx5, dx6, dx7, dx8, dx9, dx10, 
dxccs1, dxccs2, dxccs3, dxccs4, dxccs5,  female, 
hosp_nis.x,  key_nis, los, nis_stratum,  pay1,orproc,  pr1, pr2, pr3, pr4, pr5,  prccs1, prccs2, 
prccs3, prccs4, prccs5, race, totchg,  year, zipinc_qrtl, lvad)

c15.1 <- c15.1 %>% filter(amonth < 10)


# get the original core file from that year

s15 <- read_stata("G:/NIS_2015Q1Q3_Severity.dta")

names(s15) <- tolower(names(s15))

# then we will only select "cm" variables and "nis_stratum".


s15_s <- s15 %>% select(key_nis, cm_aids:cm_wghtloss)

m15 <- left_join(c15.1, s15_s, by = "key_nis")

glimpse(m15)

```

appending all dataframes to create one large dataframe:

```{r appending all dataframes together}

# first need to change var names for few var to common
# then append

m10 <- m10 %>% rename(hosp_nis = hospid, key_nis = key)

m11 <- m11 %>% rename(hosp_nis = hospid, key_nis = key)

m15 <- m15 %>% rename(hosp_nis = hosp_nis.x)


# append

df <- rbind(m10, m11, m12, m13, m14, m15) # dataframe for all years 2010 - 2015

glimpse(df)

```

1. create standard variables and do some data munging to create new variables

2. seperate dataframe into quarters for each year to determine prop of admissions for each quarter and then prop of gib for each quarter

3. determine basic trends and outcome for gib admissions when compared to other admission types

4. determine resource utilization procedures performed, blood transfusion and transfer to acute rehab etc for gib patients

5. also provide those admissions that result in transplant , however would be very small I think 

6. use only gib as primary diagnosis for admission = hence most important cause for admission

```{r}

gib <- as.character(c('53100','53101','53120', '53121', '53140', '53141', '53160', '53161', '53200', '53201',
'53220', '53221', '53240', '53241','53260', '53261', '53300', '53301', '53320', '53321',
'53340', '53341', '53360', '53361', '53400', '53401', '53420', '53421', '53440', '53441',
'53460', '53461', '153',"5781","5789",'53783',"56985",
'4550', '4551', '4552', '4553', '4554', '4555', '4556', '4557', '4558', '4559',"53541", "56982"))

df$gib <- with(df, ifelse((dx1 %in% gib | dx2 %in% gib), 1, 0))

df %>% count(gib) # count of admissions for primary gi bleeding in the entire cohort
```



```{r divide df into quarters of study}


                      
                      
df$qrtr[df$amonth %in% 1:3] <- "a"
df$qrtr[df$amonth %in% 4:6] <- "b"
df$qrtr[df$amonth %in% 7:9] <- "c"
df$qrtr[df$amonth %in% 10:12] <- "d"

df %>% count(qrtr) # created quarter of admissions for each year

df <- df %>% tidyr::drop_na(qrtr)

df %>% count(year) # determined data on year of admissions

df$year_n <- df$year

df <- df %>% unite(time, year, qrtr)

df %>% count(time)


write_csv(df, "G:/lvad_gib/df_touse.csv") # save the most updated df 
```








```{r create table one to determine differences between admissions for gib and other admissions}

# will initially need to create and modify some variables


df <- df %>% mutate(transf = fct_recode(factor(dispuniform),
                                               "home" = "1",
                                               "ltac" = "2",
                                               "snf" = "5",
                                               "hhc" = "6",
                                              "died" = "20",
                                               "ama" = "7"))


df$transf[df$transf == "99"]<- NA


df <- df %>% mutate(insur = fct_recode(factor(pay1),
                    "medicare" = "1",
                    "medicaid" = "2",
                    "private" = "3",
                    "self" = "4",
                    "others" = "6"))


df$insur[df$insur == "5"]<- NA


df <- df %>% mutate(race_n = fct_recode(factor(race),
                    "caucasian" = "1",
                    "aa" = "2",
                    "hispanic" = "3",
                    "others" = "4",
                    "others" = "6",
                    "others" = "5"))

df %>% count(race_n)

df %>% count(insur)

df %>% count(transf)

write_csv(df, "G:/lvad_gib/df_touse.csv") # save the most updated df 
```



```{r af}

af <- as.character(c("42731"))

df$af <- with(df, ifelse((dx1 %in% af | dx2 %in% af | dx3 %in% af | dx4 %in% af | dx5 %in% af), 1, 0))

df %>% count(af)
```

```{r }

cns <- as.character(c("431","43411","0389","43491","7802",'43301', '43311', '43321', '43331',
                      '43381', '43391', '4340', '43400', '43401', '4341',
'43410', '43411', '4349', '43490', '43491',"7802","34660", "34661", "34662", "34663", "436", "430", "78097"))
                

df$cns <- with(df, ifelse((dx1 %in% cns | dx2 %in% cns | dx3 %in% cns), 1, 0))

df %>% count(cns)

```

```{r infection}
inf <- as.character(c('0380',
'0381', '03810', '03811', '03812', '03819',          
'03842',                  
'03840', '03841', '03843', '03844', '03849',          
'0031', '0202', '0223', '0362', '0382', '0383', '0545',      
'0388',' 0389', '449', '77181', '7907', '99591', '99592',      
'0200', '0208', '0209', '0218', '0219', '0228', '0229', '0230', '0231', '0232',
'0233', '0238', '0239', '024', '025', '0260', '0269', '0270', '0271', '0272',
'0278', '0279', '0300', '0301', '0302', '0303', '0308', '0309', '0312', '0318',
'0319', '03289', '0329', '0330', '0331', '0338', '0339', '0341', '0363', '03681',
'03689', '0369', '037', '0392', '0393', '0394', '0398', '0399', '0400', '0401',
'0402', '0403', '04042', '04081', '04082', '04089', '0410', '04100', '04101', '04102',
'04103', '04104', '04105', '04109', '0411', '04110', '04111', '04112', '04119', '0412',
'0413', '0414', '04141', '04142', '04143', '04149', '0415', '0416', '0417', '0418',
'04181', '04182', '04183', '04184', '04185', '04186', '04189', '0419', '390', '3929',
'7953', '79531', '79539', 'V090', 'V091', 'V092', 'V093', 'V094', 'V0950', 'V0951',
'V096', 'V0970', 'V0971', 'V0980', 'V0981', 'V0990', 'V0991', 'V1204', "78060", "99932"))   

```



```{r primary diagnosis infection}

df$infection <- with(df,ifelse ((dx1 %in% inf | dx2 %in% inf | dx3 %in% inf | dx4 %in% inf | dx5 %in% inf), 1,0))

df %>% count(infection) 
```
```{r acute respiratory failure}

resp <- as.character(c('51881', '51884', "51881","49121","51884"))

df$resp <- with(df, ifelse((dx1 %in% resp | dx2 %in% resp | dx3 %in% resp), 1, 0))

df %>% count(resp)

```


```{r arrythmias}
arry <- as.character(c('4270',  '4271','42731','42741', '42742', '4275','4272', '42789', '4279', '7850', '7851')) 

df$arry <- with(df, ifelse((dx1 %in% arry | dx2 %in% arry), 1, 0)) 

df %>% count(arry)
```
```{r}
df$cause[df$cns == 1] <- "cns"
df$cause[df$resp == 1]<- "resp"
df$cause[df$gib == 1]<- "gib"
df$cause[df$infection == 1]<- "infection"
df$cause[df$arry == 1]<- "arry"

df %>% count(cause)


```


```{r}
library(tableone)

vars <- c("age",  "transf", "insur","race_n", "infection","resp","arry",
"female",  "los",  "totchg", "cm_anemdef",  "cm_bldloss", 
"cm_chrnlung", "cm_coag",  "cm_dm", "cm_dmcx", "cm_htn_c", "cm_hypothy", "cm_liver",  "cm_lytes", "cm_mets", "cm_neuro", "cm_obese", "cm_para", "cm_perivasc", "af","cns",
  "cm_renlfail",  "cm_ulcer", "cm_wghtloss",  "gib", "qrtr","totchg")

factorvars = c(  "transf", "insur","race_n",  
"female",   "cm_anemdef",  "cm_bldloss", "af","cns","infection","resp","arry",
"cm_chrnlung", "cm_coag",  "cm_dm", "cm_dmcx", "cm_htn_c", "cm_hypothy", "cm_liver",  "cm_lytes", "cm_mets", "cm_neuro", "cm_obese", "cm_para", "cm_perivasc",  "cm_renlfail",  "cm_ulcer", "cm_wghtloss",  "gib", "qrtr")

# create survey design object

svyd <- survey::svydesign(data = df, nest = T, weights = ~discwt, strata = ~nis_stratum, ids = ~hosp_nis)

options(survey.lonely.psu = "certainty")

t1 <- tableone::svyCreateTableOne(vars = vars,factorVars = factorvars, strata = c("gib"),data = svyd,includeNA = FALSE)

tableone <- print(t1)

#write.csv(tableone, "G:/lvad_gib/table_one.csv")
```

```{r}
df$cause[df$cns == 1] <- "cns"
df$cause[df$resp == 1]<- "resp"
df$cause[df$gib == 1]<- "gib"
df$cause[df$infection == 1]<- "infection"
df$cause[df$arry == 1]<- "arry"

df %>% count(cause)
```





```{r create survey object}

dfs <- df %>% srvyr::as_survey_design(weight = discwt, strata = nis_stratum, id = hosp_nis, nest = T)

dfs

options(survey.lonely.psu = "certainty")

```


```{r}

# overall % of admissions for gib

dfs %>%
  summarise(total = survey_mean(gib, vartype = "ci"))


# proportional trends for admissions for GIB per study period quarter

gi_prop <- dfs %>% 
  group_by(year_n) %>%
  summarise(prop = survey_mean(gib, vartype = "ci", na.rm = T)) 
   

gib_total <- dfs %>%
  group_by(year_n) %>%
  summarise(total = srvyr::survey_total(gib, vartype = "ci", na.rm = TRUE))



```



```{r}
 
gibonly <- df %>%
  filter(gib == 1) 
  
gisurvey <- gibonly %>% srvyr::as_survey_design(weight = discwt, strata = nis_stratum, id = hosp_nis, nest = T)


  
gisurvey %>%
  summarise(infection = survey_mean(infection))

gisurvey %>%
  summarise(cns = survey_mean(cns))

gisurvey %>%
  summarise(arry = survey_mean(arry))



```

primary procedures performed in the gib patients:

```{r}

gibonly %>%
  count(pr1) %>%
  arrange(desc(n))

gibonly %>%
   count(prccs1) %>%
  arrange(desc(n))

```

45.13 = small bowel endoscopy NEC
44.43 = endoscopic control of gastric bleeding
99.04 = blood prbc transfusion
45.23 = colonoscopy
45.16 = ogdscopy with closed biopsy
45.43 = endoscopic destruction of large intestine lesion
45.34 = endoscopic destruction of small bowel lesions
45.42 = endoscopic large bowel polyp removal
43.41 = gastric polpys removal
45.25 = closed large bowel biopsy
38.97 = Cardiac catheter placement (swan, cvp line)
38.93 = cvp line
45.19 = small bowel diagnostic procedure nec
88.72 = ECHO
37.51 = transplant
37.21 = RHC
39.95 = hemodialysis
39.98 = hemorhage control
88.47 = CT angiogram of abdomen/pelvis
45.30 = endoscopic lesion duodenal therapy
45.14 = endoscopic biopsy of small intestine 
17.33 = laprascopic right hemicolectomy
37.98 = AICD change
43.49 = local gastric desctruction NEC
44.44 = transcatheter gastric embolization
45.73 = right hemicolectomy
88.01 = CT abdomen/pelvis
99.05 = platelet transf
99.07 = FFP transf
99.19 = local anticoagulant injection
44.13 = gastroscopy
44.49 = control gastric hemorrage
45.24 = endscopy large bowel
45.33 = small bowel local excsion
45.62 = small bowel resection
46.51 = small bowel stoma closure
48.33 = laser rectal polyps destruction
48.36 = endscopic removal polpys rectum
48.99 = rectal/perirectal procedures
51.23 = lap chole
54.59 = lapratomy
54.91 = abdominal paracentesis
88.42 = contrast angiogram

```{r}
bloodp <- as.character(c("9905","9907","9904"))

large_b <- as.character(c("4524", "4573","1733","4525","4542","4523"))

small_b <- as.character(c("4651","4562","4533","4514","4530","4519","4534","4513"))

rectal_p <- as.character(c("4899","4836"))

ogdsc <- as.character(c("4449","4413","4349","4530","4341","4443"))

```


```{r}


df$bloodp <- with(df, ifelse((pr1 %in% bloodp | pr2 %in% bloodp | pr3 %in% bloodp | pr4 %in% bloodp | pr5 %in% bloodp), 1, 0))

df %>% count(bloodp)

df$large_b <- with(df, ifelse((pr1 %in% large_b | pr2 %in% large_b | pr3 %in% large_b | pr4 %in% large_b | pr5 %in% large_b), 1, 0))

df %>% count(large_b)

df$small_b <- with(df, ifelse((pr1 %in% small_b | pr2 %in% small_b | pr3 %in% small_b | pr4 %in% small_b | pr5 %in% small_b), 1, 0))

df %>% count(small_b)

df$rectal_p <- with(df, ifelse((pr1 %in% rectal_p | pr2 %in% rectal_p | pr3 %in% rectal_p | pr4 %in% rectal_p | pr5 %in% rectal_p), 1, 0))

df %>% count(rectal_p)

df$ogd <- with(df, ifelse((pr1 %in% ogdsc | pr2 %in% ogdsc | pr3 %in% ogdsc | pr4 %in% ogdsc | pr5 %in% ogdsc), 1, 0))

df %>% count(ogd)

open <- as.character(c("545","4562","4573","1733"))

df$open <- with(df, ifelse((pr1 %in% open | pr2 %in% open | pr3 %in% open | pr4 %in% open | pr5 %in% open), 1, 0))

df %>% count(open)


df$proc <- with(df, ifelse((large_b == 1 | small_b == 1 | rectal_p == 1 | ogd == 1 | open == 1), 1, 0))

df %>% count(proc)

```


```{r}
# survey results for gi procedures in patients with gib:

gibonly <- df %>%
  filter(gib == 1) 
  
gisurvey <- gibonly %>% srvyr::as_survey_design(weight = discwt, strata = nis_stratum, id = hosp_nis, nest = T)

gisurvey %>%
  summarise(ogd = survey_mean(ogd))# upper gi scopy


gisurvey %>%
  summarise(large_b = survey_mean(large_b)) # large bowel 

gisurvey %>%
  summarise(small_b = survey_mean(small_b)) # small bowel 

gisurvey %>%
  summarise(rectal_p = survey_mean(rectal_p)) # rectal procedures


gisurvey %>%
  summarise(open = survey_mean(open))

gisurvey %>%
  summarise(proc = survey_mean(proc))


gisurvey %>%
  group_by(year_n) %>%
  summarise(procedure = survey_mean(proc))


```

Am going to join the corresponding c-c files to obtain cost for each year and then use that for survey analysis.

```{r getting cost files }

# year 2010

df2010 <- df %>%
  filter(year_n == 2010)

cc2010 <- read_csv("G:/cc_nis/cc2010NIS.csv")

cc2010$hosp_nis <- cc2010$hospid 


df2010_2 <- left_join(df2010, cc2010, by = "hosp_nis")

df2010_2$apicc <- as.numeric(df2010_2$apicc)

df2010_2 <- df2010_2 %>% mutate(charges = totchg*apicc)

summary(df2010_2$charges)

```


```{r}
# year 2011

df2011 <- df %>%
  filter(year_n == 2011)

cc2011 <- read_csv("G:/cc_nis/cc2011NIS.csv")

cc2011 <- cc2011 %>% rename(hosp_nis = hospid) 


df2011_2 <- left_join(df2011, cc2011, by = "hosp_nis")


df2011_2$apicc <- as.numeric(df2011_2$apicc)

df2011_2 <- df2011_2 %>% mutate(charges = totchg*apicc)

summary(df2011_2$charges)


```


```{r}
# year 2012

df2012 <- df %>%
  filter(year_n == 2012)

cc2012 <- read_csv("G:/cc_nis/cc2012nis.csv")

cc2012$hosp_nis <- as.numeric(cc2012$hosp_nis)

df2012_2 <- left_join(df2012, cc2012, by = "hosp_nis")

df2012_2$ccr_nis <- as.numeric(df2012_2$ccr_nis)

df2012_2 <- df2012_2 %>% mutate(charges = totchg*ccr_nis)

summary(df2011_2$charges)
```



```{r}
# year 2013

df2013 <- df %>%
  filter(year_n == 2013)

cc2013 <- read_csv("G:/cc_nis/cc2013NIS.csv")

 cc2013$hosp_nis <- as.numeric(cc2013$hosp_nis)

df2013_2 <- left_join(df2013, cc2013, by = "hosp_nis")

df2013_2$ccr_nis <- as.numeric(df2013_2$ccr_nis)

df2013_2 <- df2013_2 %>% mutate(charges = totchg*ccr_nis)

summary(df2013_2$charges)
```

```{r}
# year 2014

df2014 <- df %>%
  filter(year_n == 2014)

cc2014 <- read_csv("G:/cc_nis/cc2014NIS.csv")

df2014_2 <- left_join(df2014, cc2014, by = "hosp_nis")

df2014_2$ccr_nis <- as.numeric(df2014_2$ccr_nis)

df2014_2 <- df2014_2 %>% mutate(charges = totchg*ccr_nis)

summary(df2014_2$charges)
```

```{r}
# year 2015

df2015 <- df %>%
  filter(year_n == 2015)

cc2015 <- read_csv("G:/cc_nis/cc2015NIS.csv")

cc2015$hosp_nis <- as.numeric(cc2015$hosp_nis)

df2015_2 <- left_join(df2015, cc2015, by = "hosp_nis")

df2015_2$ccr_nis <- as.numeric(df2015_2$ccr_nis)

df2015_2 <- df2015_2 %>% mutate(charges = totchg*ccr_nis)

summary(df2015_2$charges)
```


```{r}
# saving dataframes for each year with cc file merged
# saving the large df dataframe again with all variables included till now

#write_csv(df, "G:/lvad_gib/data/dflarge.csv")

#write_csv(df2010_2, "G:/lvad_gib/data/cc2010.csv")

#write_csv(df2011_2, "G:/lvad_gib/data/cc2011.csv")

#write_csv(df2012_2, "G:/lvad_gib/data/cc2012.csv")

#write_csv(df2013_2, "G:/lvad_gib/data/cc2013.csv")

#write_csv(df2014_2, "G:/lvad_gib/data/cc2014.csv")

#write_csv(df2015_2, "G:/lvad_gib/data/cc2015.csv")
```

outcome in patients who needed procedure:

```{r}

# again create survey object for only gib patients

gibonly <- df %>%
  filter(gib == 1) 
  
gisurvey <- gibonly %>% srvyr::as_survey_design(weight = discwt, strata = nis_stratum, id = hosp_nis, nest = T)


# create traditional survey object 

gisurv <- survey::svydesign(data = gibonly, ids = ~hosp_nis, strata = ~nis_stratum, nest = T, weights = ~discwt)


gisurvey %>%
  group_by(proc) %>%
  summarize(died = survey_mean(died))

svychisq(~proc + died, design = gisurv)


gisurvey %>%
  group_by(proc) %>%
  summarise(los = survey_mean(los))

svyttest(los ~ proc, design = gisurv)
```

charges and comparison of charges for intervention and nonintervention cohorts:

```{r}

# charges for gib patients for each year



options(survey.lonely.psu = "certainty")

ch2010 <- 
  df2010_2 %>%
  filter(gib == 1) %>%
  tidyr::drop_na(charges) %>%
  srvyr::as_survey_design(weight = discwt, strata = nis_stratum, id = hosp_nis, nest = T) %>%
  group_by(proc) %>%
  summarise(charge = survey_mean(charges))

ch2011 <-
df2011_2 %>%
  filter(gib == 1) %>%
  tidyr::drop_na(charges) %>%
  srvyr::as_survey_design(weight = discwt, strata = nis_stratum, id = hosp_nis, nest = T) %>%
  group_by(proc) %>%
  summarise(charge = survey_mean(charges))

ch2012 <- 
df2012_2 %>%
  filter(gib == 1) %>%
  tidyr::drop_na(charges) %>%
  srvyr::as_survey_design(weight = discwt, strata = nis_stratum, id = hosp_nis, nest = T) %>%
  group_by(proc) %>%
  summarise(charge = survey_mean(charges))

ch2013 <- 
df2013_2 %>%
  filter(gib == 1) %>%
  tidyr::drop_na(charges) %>%
  srvyr::as_survey_design(weight = discwt, strata = nis_stratum, id = hosp_nis, nest = T) %>%
  group_by(proc) %>%
  summarise(charge = survey_mean(charges))

ch2014 <- 
df2014_2 %>%
  filter(gib == 1) %>%
  tidyr::drop_na(charges) %>%
  srvyr::as_survey_design(weight = discwt, strata = nis_stratum, id = hosp_nis, nest = T) %>%
  group_by(proc) %>%
  summarise(charge = survey_mean(charges))

ch2015 <-
df2015_2 %>%
  filter(gib == 1) %>%
  tidyr::drop_na(charges) %>%
  srvyr::as_survey_design(weight = discwt, strata = nis_stratum, id = hosp_nis, nest = T) %>%
  group_by(proc) %>%
  summarise(charge = survey_mean(charges))


totalc <- rbind(ch2010, ch2011, ch2012, ch2013, ch2014, ch2015)

t.test(charge ~ proc, data = totalc)

totalc %>%
  filter(proc == 1) %>%
  summarise(mean = mean(charge), std = 2*mean(charge_se))


totalc %>%
  filter(proc == 0) %>%
  summarise(mean = mean(charge), std = 2*mean(charge_se))


cost<- c(20261.74, 15688.68)
sd <- c(5355.61, 8721.07)
intervention <- c("yes","no")


cost <- data.frame(intervention, cost, sd) %>% tbl_df()

```





logbinomial regression to determine adjusted risk ratio for various covariates to determine risk of gib:

```{r}

library(logbin)

gib <- MASS::glm.nb(gib ~ age + race_n + insur + cm_chrnlung + af + cm_dm + cm_liver + cm_perivasc + cm_obese + cm_renlfail  , data = df)

summary(gib)

exp(coef(gib))

exp(confint(gib))

md <- broom::augment(gib)

```

```{r}
md <- md %>%
  mutate(prop = exp(.fitted)) 
```



```{r}
# create graph for paper


library(bbplot)
library(ggthemes)

age <- ggplot(data = md, aes(x = age, y = prop)) + geom_point(color = "lightgray")+ geom_smooth(color = "blue", fill = "black") + ggthemes::theme_economist_white()

age2 <- age + ylim(0,1) + xlab("Age of LVAD supported patients (years)") + ylab("Adjusted Probability of GIB Admission")

age2

```



```{r proportion undergoing intervention and procedures}

inter <- c("Upper GI","Small Bowel","Colon")
prop <- c(30,27.3,45.7)
prop_u <- c(30 + 1.8, 27.3 + 2.4, 45.7 + 3.2)
prop_l <- c(30 - 1.8, 27.3 - 2.4, 45.7 - 3.2)

data <- data.frame(inter,prop,prop_u,prop_l) %>% tbl_df()


int <- ggplot(data = data, aes(x = inter, y = prop)) + geom_bar(stat = "identity", color = "black",width = 0.5) + ylim(0,100) + theme_economist_white() + geom_errorbar(data = data, aes(ymin = prop, ymax = prop_u, width = 0.4)) 

int2 <- int + xlab("Interventions/Procedures performed") + ylab("Percetage of GIB admissions")

int3 <- int2 + geom_text(aes(y = prop + 6, label = prop)) + theme(axis.text.x = element_text(size = 8)) + theme(axis.text.y = element_text(size = 8))

int3


```

```{r graph for costs}


c <- ggplot(data  = cost, aes( x = intervention, y = cost)) + geom_bar(stat = "identity",color = "black", width = 0.3) + theme_economist_white() + geom_errorbar(data = cost, aes(ymin = cost, ymax = (cost + sd)), width = 0.1) 

c1 <- c + xlab("Interventions/Procedure performed in GIB cohort") + ylab("Adjusted Costs for each Admission (Dollars)")

c2 <- c1 + geom_text(data = cost, aes(y = (cost + sd) + 6, label = cost), vjust = -0.5) + theme(axis.text.x = element_text(size = 8)) + theme(axis.text.y = element_blank())

```



```{r arrange both into 1 frame}
library(ggpubr)


fig <- ggpubr::ggarrange(int3, age2, ncol = 2)

fig

ggsave(plot = fig,filename =  "G:/lvad_gib/data/figure.tiff", device = "tiff")

```

